### 2018-06-18 pubs/itp-2018/sections/proof-reconstruction.tex
Workflow reviewed

\documentclass[../main.tex]{subfiles}
\begin{document}

@@

The process begins with a \TPTP file that encodes a \CPL conjecture.
Then, we use the \Metis prover to generate in \TSTP format a derivation
of the proof in case the \CPL conjecture corresponds to a theorem.
If so, the process continues. The next step is in charge of the
\Athena translator tool that generates an \Agda file.
Athena first parses the \TSTP file, then analyzes its
derivation and generates a representation of the natural deduction
proof. In the analysis, some unnecessary steps read from the \TSTP derivation
are taken into account in the final proof-tree mainly because some introduce redundancies
or they do not contribute in the proof.
The Agda file genereted by \Athena uses names of functions
and theorems from the \Agda libraries that accompany this article:
\texttt{agda-prop} and \texttt{agda-metis}.

Using \Agda as the proof-checker, we type-check the proof-terms of the
\Agda file previous generated. If this type-checking success, the
\TSTP derivation generated by \Metis will be \emph{correct} module the
\Agda correctness and the proposed formalisation.
In such a case, \Agda will output an interface file. Otherwise, when
the type-checking fails, the failure must be investigated by the user.
The possible causes can be due to many factors: a
\emph{completeness} issue in our \Agda libraries for the \Metis
reasoning, a translation bug in \Athena, errors in \Agda, printing or
soundness bugs in the \Metis prover.

In the remainder part of this section, we present a formal description
of definitions and theorems necessary to reconstruct \Metis inference
rules. Through this description, we refer to the lines in the \Metis
derivation presented in Fig.~\ref{complete-metis-example} of the
theorem in \eqref{eq:complete-example-problem} to show each rule.

>>>>

\documentclass[../itp-2018.tex]{subfiles}
\begin{document}

@@

The process begins assuming that the user posses a \TPTP valid file that encodes
a \CPL conjecture. If this conjecture is a theorem, by means of \Metis, we
obtain a derivation in \TSTP format of a proof for this conjecture. Now, we use
the \Athena tool to generate the \Agda file that corresponds to the proof-term
for such \TSTP derivation. \Athena parses and prunes the proof-tree of the \TSTP
derivation by removing some redundancies and steps that do not contribute in the
proof. After this translation process, we end up with a proof-term  in the \Agda
file of the natural deduction proof. This \Agda file will make calls to theorems
and lemmas from the \Agda libraries, \texttt{agda-prop} (classical propositional
logic) and \texttt{agda-metis} (propositional reasoning for \Metis derivations).

Using \Agda as the proof-checker, we type-check the proof-terms of the \Agda
file previous generated. If this type-checking success, the \TSTP derivation
generated by \Metis will be \emph{correct} module the \Agda correctness and the
proposed formalisation. In such a case, \Agda will output an interface file.
Otherwise, \Agda will report where the type-checking fails, if it is the case,
the failure must be investigated by the user. The possible causes can be due to
many factors: \emph{completeness} issues in our \Agda libraries for the \Metis
reasoning, bugs in the translation by \Athena, bugs in \Agda, printing errors
of the \TSTP derivation by \Metis or soundness bugs in the \Metis
reasoning.

In the remainder part of this section, we present a formal description of
definitions and theorems necessary to reconstruct \Metis inference rules.
Through this description, we refer to the lines in the \Metis derivation
presented in Fig.~\ref{complete-metis-example} of the theorem in
\eqref{eq:complete-example-problem} to show examples of each rule.
